---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

# Import data from published CSV URL
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRYa7ohrdH_tvXAudXrFuBQ3-2EiJAl5rWsdooDC6YNAxHJErchPRhEHZKnYUV2d1t57AhpUN4daD-a/pub?gid=914579388&single=true&output=csv")

# Rename variables and create new data frame
latest_data <- logged_data %>%
  rename(
    device_type = "What device are you using when viewing YouTube recommendations?",
    logged_in_status = "Are you logged into a YouTube/Google account when seeing these recommendations?",
    unusualness_logged_in = "Rate the unusualness of the recommended video(s) on a scale from 1-5...4",
    categories_logged_in = "What characteristics describe these recommendations? (Select all that apply)...5",
    unusualness_not_logged_in = "Rate the unusualness of the recommended video(s) on a scale from 1-5...6",
    categories_not_logged_in = "What characteristics describe these recommendations? (Select all that apply)...7",
    unusual_recommendations_count = "How many recommendations seemed unusual to you? Type 0 if none were unexpected"
  )
```

```{css}
/* Style the headers for better readability */
h1, h2, h3 {
    font-family: Impact, fantasy;
    color: #d4a373;
    border-bottom: 2px solid #7A6E51;
    padding-bottom: 5px;
}

/* Apply a modern, clean font to the entire document */
body {
    font-family: Arial, sans-serif;
    line-height: 1.6;
    background-color: #EEE5D3; /* Beige background */
    color: #333;
    padding: 20px;
}

/* Style images to have a subtle shadow and spacing */
img {
    display: block;
    margin: 20px auto;
    border-radius: 8px;
    box-shadow: 2px 2px 10px rgba(0, 0, 0, 0.1);
}
```

## Analysis of YouTube Recommendation Data

This report tracks unusualness ratings and categories of YouTube video recommendations for users who are logged in versus not logged in.

### Unusualness Ratings: Logged-in vs. Non-Logged-in Users

```{r}
# Create new data frame with "login_status" column to differentiate logged-in and non-logged-in users
data_for_plot <- data.frame(
  login_status = c(rep("Logged In", length(latest_data$unusualness_logged_in)),
                   rep("Not Logged In", length(latest_data$unusualness_not_logged_in))),
  unusualness = c(latest_data$unusualness_logged_in, latest_data$unusualness_not_logged_in)
)

# Plot bar chart for unusualness ratings (logged in vs. not logged in users)
ggplot(data_for_plot, aes(x = unusualness, fill = login_status)) +
  geom_bar(position = "dodge") +
  labs(
    title = "Unusualness Ratings of YouTube video recommendations",
    subtitle = "Logged-in vs. Non-Logged-in Users",
    x = "Unusualness (1 = Completely expected, 5 = Extremely surprising or out of context)",
    y = "Frequency of Responses"
  ) +
  theme_grey()
```

### Categories Recommended for Logged-in Users

```{r}
# Create new data frame for logged-in users' categories (separate and count)
data_for_logged_in <- latest_data %>%
  filter(categories_logged_in != "N/A") %>%
  separate_rows(categories_logged_in, sep = ",") %>%
  count(categories_logged_in)  # Count frequency of each category for logged-in users

# Plot bar chart for frequency of categories recommended for logged-in users
ggplot(data_for_logged_in, aes(x = categories_logged_in, y = n, fill = categories_logged_in)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Frequency of Categories Recommended for Logged-in Users",
    x = "Categories Recommended",
    y = "Frequency of Responses"
  ) +
  theme_grey() +
  theme(
    axis.text.x = element_blank()  # Remove x-axis labels
  )
```

### Categories Recommended for Non-Logged-in Users

```{r}
# Create new data frame for non-logged-in users' categories (separate and count)
data_for_not_logged_in <- latest_data %>%
  filter(categories_not_logged_in != "N/A") %>%
  separate_rows(categories_not_logged_in, sep = ",") %>%
  count(categories_not_logged_in)  # Count frequency of each category for non-logged-in users

# Plot bar chart for frequency of categories recommended for non-logged-in users
ggplot(data_for_not_logged_in, aes(x = categories_not_logged_in, y = n, fill = categories_not_logged_in)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Frequency of Categories Recommended for Non-Logged-in Users",
    x = "Categories Recommended",
    y = "Frequency of Responses"
  ) +
  theme_grey() +
  theme(
    axis.text.x = element_blank()  # Remove x-axis labels
  )
```

### Summary Values

```{r}
# Calculate summary statistics for unusualness ratings (min, max, mean)
summary_values <- latest_data %>%
  summarise(
    min_unusualness_logged_in = min(unusualness_logged_in, na.rm = TRUE),  # Min value for logged-in users
    max_unusualness_logged_in = max(unusualness_logged_in, na.rm = TRUE),  # Max value for logged-in users
    mean_unusualness_logged_in = mean(unusualness_logged_in, na.rm = TRUE),  # Mean for logged-in users
    min_unusualness_not_logged_in = min(unusualness_not_logged_in, na.rm = TRUE),  # Min value for non-logged-in users
    max_unusualness_not_logged_in = max(unusualness_not_logged_in, na.rm = TRUE),  # Max value for non-logged-in users
    mean_unusualness_not_logged_in = mean(unusualness_not_logged_in, na.rm = TRUE),  # Mean for non-logged-in users
  )
```

The average unusualness rating for logged-in users is `r round(summary_values$mean_unusualness_logged_in, 2)`. 
For non-logged-in users, the average unusualness rating is `r round(summary_values$mean_unusualness_not_logged_in, 2)`.

This data suggests that logged-in users may receive more unexpected recommendations compared to non logged-in users, which could indicate that personalised YouTube algorithms are giving them more tailored content which may feel more surprising or unexpected. In contrast, non logged-in users may receive more generic recommendations that align with a broader audience's expectations.
